Paper Figures and Text

### 2023-02-02 Fish Data Analysis/Paper_Figures.qmd
Testing 3D vs 2D graphs

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") %>%
                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))

>>>>

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") #%>%
                                             #select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))
